An algorithmic framework for generating contour parallel toolpaths with adaptive extrusion width for additive manufacturing

### 2019-08-26 4_method.tex
Juns new overview section

\begin{figure*}
\centering
\setlength{\figheight}{.15\textwidth}
\setlength{\figwidth}{.15\textwidth}
\setlength{\figwidthTwo}{.22\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/input.pdf}
\caption{Layer outline}\label{}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/uoc.pdf}
\caption{Skeleton}\label{}
\end{subfigure}
\begin{subfigure}{\figwidthTwo}\centering
\hspace*{\tempheightTwo}
\includegraphics[height=\figheight]{sources/method/overview/surface/UoC_with_cones.png}
\caption{Union of Cones}\label{}
\end{subfigure}
\begin{subfigure}{\figwidthTwo}\centering
\hspace*{\tempheightTwo}
\includegraphics[height=\figheight]{sources/method/overview/surface/sliced_naive_cropped.png}
\caption{Slicing}\label{}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/naive.png}
\caption{Uniform paths}\label{}
\end{subfigure}

\setlength{\figwidth}{.22\textwidth}
\setlength{\figwidthTwo}{.17\textwidth}
\setlength{\figwidthTree}{.22\textwidth}
\setlength{\tempheight}{-0.3cm}
\setlength{\tempheightTwo}{-0.5cm}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[height=\figheight]{sources/method/overview/surface/marking_cropped.png}

@@

\includegraphics[width=\figheight]{sources/method/overview/2D/marked.pdf}
\caption{Center identification}\label{3d_surface_overview_center}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[height=\figheight]{sources/method/overview/surface/rounded_cropped.png}

@@

\includegraphics[width=\figheight]{sources/method/overview/2D/rounded.pdf}
\caption{Quantization}\label{3d_surface_overview_rounded}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[height=\figheight]{sources/method/overview/surface/smoothed_cropped.png}

@@

\includegraphics[width=\figheight]{sources/method/overview/2D/smoothed.pdf}
\caption{Smoothing}\label{3d_surface_overview_smoothed}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[height=\figheight]{sources/method/overview/surface/sliced_cropped.png}

@@

\includegraphics[width=\figheight]{sources/method/overview/2D/sliced.png}
\caption{Adaptive width paths}\label{3d_surface_overview_sliced}
\end{subfigure}
\caption{
A geometrical conceptualization of our technique.
3D visualization on top and the corresponding 2D visualization on bottom.
In the UoC \subref{3d_surface_overview_uoc}
we mark the central regions \subref{3d_surface_overview_center}
and quantize the height in those regions \subref{3d_surface_overview_rounded}.
We then smooth out the jumps between different integer multiples \subref{3d_surface_overview_smoothed}
and finally we slice the structure to get the toolpaths \subref{3d_surface_overview_sliced}.
Blue signifies regions marked as being central.
The numbers are the integer multiples of half the nozzle width.
}
\label{3d_surface_overview}
\end{figure*}

>>>>

\begin{figure*}
\centering
\setlength{\figwidth}{.18\textwidth}
\setlength{\figwidthTwo}{.17\textwidth}
\setlength{\figwidthTree}{.22\textwidth}
\setlength{\tempheight}{-0.3cm}
\setlength{\tempheightTwo}{-0.5cm}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[width=\figwidthTree]{sources/method/surface/union_of_cones_cropped.png}

@@

\includegraphics[width=\figwidthTwo]{sources/method/surface/uoc.pdf}
\caption{Union of Cones}\label{3d_surface_overview_uoc}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[width=\figwidthTree]{sources/method/surface/marking_cropped.png}

@@

\includegraphics[width=\figwidthTwo]{sources/method/surface/marked.pdf}
\caption{Center}\label{3d_surface_overview_center}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[width=\figwidthTree]{sources/method/surface/rounded_cropped.png}

@@

\includegraphics[width=\figwidthTwo]{sources/method/surface/rounded.pdf}
\caption{Quantized}\label{3d_surface_overview_rounded}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[width=\figwidthTree]{sources/method/surface/smoothed_cropped.png}

@@

\includegraphics[width=\figwidthTwo]{sources/method/surface/smoothed.pdf}
\caption{Smoothed}\label{3d_surface_overview_smoothed}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[width=\figwidthTree]{sources/method/surface/sliced_cropped.png}

\includegraphics[width=\figwidthTwo]{sources/method/surface/sliced_2D.png}
\caption{Sliced}\label{3d_surface_overview_sliced}
\end{subfigure}
\caption{
A geometrical conceptualization of our technique.
3D visualization on top and the corresponding 2D visualization on bottom.
In the UoC \subref{3d_surface_overview_uoc}
we mark the central regions \subref{3d_surface_overview_center}
and quantize the height in those regions \subref{3d_surface_overview_rounded}.
We then smooth out the jumps between different integer multiples \subref{3d_surface_overview_smoothed}
and finally we slice the structure to get the toolpaths \subref{3d_surface_overview_sliced}.
Blue signifies regions marked as being central.
The numbers are the integer multiples of half the nozzle width.
}
\label{3d_surface_overview}
\end{figure*}
